Scalar_M1

### 2015-05-21 analysis/e5_analysis.Rmd
model revs
different take on informativity metric from e5. Looking at % in top agreement (4 or 5 on likert)

```{r}
ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            judgment = mean(judgment), 
            p = (judgment - 1)/4)

pdf("plots/e5.pdf", width=8, height = 5)
qplot(x = stars, y = judgment, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = judgment - cil, 
                     ymax = judgment + cih)) + 
  facet_wrap(~scale)
dev.off()
```

@@

```{r}
qplot(stars, judgment, facets = degree ~ scale, 
      geom="bar", stat = "identity",
      binwidth = 1, data=ms)
```

>>>>

```{r}
n = length(unique(d$workerid))

ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            judgment = mean(judgment), 
            p = (judgment - 1)/4)
write.csv(ms, "models/e5.csv", row.names=FALSE)

# Different take on speaker.p
ma <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(speaker.p = mean( ifelse( (judgment >= 4), 1, 0)))
write.csv(ma, "models/e5a.csv", row.names=FALSE)

#Original lexical semantics plot
pdf("plots/e5.pdf", width=8, height = 5)
qplot(x = stars, y = judgment, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = judgment - cil, 
                     ymax = judgment + cih)) + 
  facet_wrap(~scale)
dev.off()

#New lexical semantics plot
qplot(x = stars, y = speaker.p, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ma) + facet_wrap(~scale)
```

@@

```{r}
qplot(stars, judgment, facets = degree ~ scale, 
      geom="bar", stat = "identity",
      binwidth = 1, data=ms)

qplot(stars, p, facets = degree ~ scale, 
      geom="bar", stat = "identity",
      binwidth = 1, data=ma)
```

### 2015-05-21 models/Model_Playspace.Rmd
different take on informativity metric from e5. Looking at % in top agreement (4 or 5 on likert)

$$ p_{L_p} (r \mid u) \propto \frac{p_S(u | r) p_{L_0}(r)}{\sum_{u' \in alts}{p_S(u' \mid r) p_{L_0}(r)}}$$

@@

```{r}
priors = read.csv("models/prior.csv")
speaker = read.csv("models/speaker.csv")
listener = read.csv("models/listener.csv")
```

@@

  if (usenone) {
    mat$none <- c(.8, .2, 0, 0, 0)
    mat$bad <- c(.25, .5, .25, 0, 0)

  }

@@

run it.

```{r}
md <- data %>%
  do(run.rsa(., alpha = 10, useprior = FALSE, usenone = TRUE))

qplot(stars, listener.p, col=degree, 
      data = md, main="Model vs Human judgments") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 2)
```

## DATA / PLOTS

@@

SOME
```{r}
d.some.unif.priors = sapply(1:5, FUN=function(i){
  norm.post("some", i, scale.matrix, unif.priors)})
d.some.raw.priors = sapply(1:5, FUN=function(i){
  norm.post("some", i, scale.matrix, raw.priors)})

qplot(c(1:5), d.some.raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="Some Posteriors")
```

ALL
```{r}
d.all.raw.priors = sapply(1:5, FUN=function(i){
  norm.post("all", i, scale.matrix, raw.priors)})
d.all.unif.priors = sapply(1:5, FUN=function(i){
  norm.post("all", i, n.scale.matrix, unif.priors)})

qplot(c(1:5), d.all.raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="All Posteriors, Raw priors")
```

>>>>

$$p_{L_p} (r \mid u) \propto \frac{p_S(u | r) p_{L_0}(r)}{\sum_{u' \in alts}{p_S(u' \mid r) p_{L_0}(r)}}$$

@@

```{r}
priors = read.csv("models/prior.csv")
# Possible transformations
#priors$prior.p = sqrt(priors$prior.p)/(sum(sqrt(priors$prior.p)))
priors$prior.p = (1/(-log(priors$prior.p))) / sum((1/(-log(priors$prior.p))))

speaker = read.csv("models/speaker.csv")
speaker.alt = read.csv("models/e5a.csv")
listener = read.csv("models/listener.csv")
```

@@

  if (usenone) {
    mat$none <- c(.8, .2, 0, 0, 0)
    mat$bad <- c(.25, .5, .25, 0, 0)
  }

@@

## RUN MODEL

```{r}
# Which alpha has tightest correlation with human judgements
alphas = seq(from=1, to=20)
fit = sapply(alphas, FUN=function(n) {
  md <- data %>%
    do(run.rsa(., alpha = n, useprior = FALSE, usenone = TRUE))

  mean((md$pred - md$listener.p)^2)
})
qplot(alphas, fit, main="MSE for alpha values", ylab="MSE")
best.alpha = which(fit == min(fit))
best.alpha

# RUN MODEL
md <- data %>%
  do(run.rsa(., alpha = best.alpha, useprior = FALSE, usenone = TRUE))
```

## DATA / PLOTS ------------>

```{r}
# Facets all scales, Model vs Human judgements
qplot(stars, listener.p, col=degree, 
      data = md, main="Model vs Human judgments") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 2)

ggplot(md, aes(x=listener.p, y=pred)) +
    geom_point(aes(colour = stars)) +
    geom_smooth(method=lm) + ggtitle("Model pred vs Human judgment")
cor(md$pred, md$listener.p)
```

@@
